Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays

### 2020-01-16 literature.Rmd
Table number corrected

Table 3: <!--\label{tab:methods}--> Summary of features and constraints of common mapping methods used to display cancer statistics (Y=Yes, N=No, S=Sometimes).

>>>>

Table 4: <!--\label{tab:methods}--> Summary of features and constraints of common mapping methods used to display cancer statistics (Y=Yes, N=No, S=Sometimes).
